---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

Body{
  font-family: Arial
}
h2 {
  color: #2c7fb8;
}

```

## Analysis of Lunch Spending
The data collected from the survey includes information about how much students spend on lunch, where they get their lunch from, and what time they have lunch. The purpose of this report is to analyse the data to identify patterns and trends in lunch spending among students, and to provide insights into how students make decisions about their lunch choices.

```{r}
library(tidyverse)

# Load data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSNQ_Q2cRWmmlPRI_-iwKFnTyoMR3uuZppOuuwO5gZ2Q-YincJ7MNxjPDIEjOxOGs_VPUGPlhUR1pdn/pub?output=csv")

# Rename variables
latest_data <- logged_data %>%
  rename(cost = 2,
         location = 4,
         time = 5)

# Summary values
avg_cost <- mean(latest_data$cost)
max_cost <- max(latest_data$cost)
min_cost <- min(latest_data$cost)

cost_location <- ggplot(data = latest_data) +
  geom_bar(aes(x = cost, fill = location)) +
  labs(title = "Distribution of Lunch Costs by Location",
       subtitle = "How much students spend on lunch across different locations",
       caption = "Survey data collected by Student at University of Auckland",
       x = "Cost of Lunch (NZD)",
       y = "Number of Lunches")

cost_time <- ggplot(data = latest_data) +
  geom_bar(aes(x = cost, fill = time)) +
  labs(title = "Distribution of Lunch Costs by Time",
       subtitle = "How much students spend on lunch across different time of the day",
       caption = "Survey data collected by Student at University of Auckland",
       x = "Cost of Lunch (NZD)",
       y = "Number of Lunches")

#print the two plots
print(cost_location)
print(cost_time)

# Creating the dynamic comment
paste("On average, students spend ", round(avg_cost, 2),
      " NZD on lunch. The maximum recorded cost is ", max_cost,
      " NZD, while the minimum is ", min_cost, " NZD.")
```
